---
title: "Coding Experiment EDA | W241 Final Project"
author: "Arunima Kayath, Daniel Rasband, Payman Rhogani"
date: \today
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
library(magrittr)
library(ggplot2)
library(ggthemes)
library(devtools)
library(mice) #for missing value imputation
library(reshape2)
library(gridExtra)
```


```{r}
data <- read.csv("CodingExperimentFinalResults.csv")
d <- as.data.table(data)
d
```


```{r}
#PR
print(paste("Number of subjects randomized for the study:", nrow(d)))
print(paste("Number of variables:", ncol(d)))
```

```{r}
print("Variables:")
names(d)
```

```{r}
#Number of subjects in control/treatment groups in week 1
d[, .N, by=control_first]
```


```{r}
#Week 1 participants
d[, .N, by=week1_attempted]
```


```{r}
#Week 2 participants
d[, .N, by=week2_attempted]
```
```{r}
print(paste("Number of subjects who attempted both tests (week 1 and 2):", d[(week1_attempted==1) & (week2_attempted==1), .N]))
```

```{r}
print(paste("Pre-treatment attrition:", nrow(d[week1_attempted == 0])))
print(paste("Post-treatment attrition:", nrow(d[(week1_attempted==1) & (week2_attempted==0)])))
```

```{r}
#Number of subjects in control/treatment groups who attrited pre-treatment
d[(week1_attempted==0) & (week2_attempted==0),.N,keyby=control_first]
#No differen between control vs treatment groups
```

```{r}
#Number of subjects in control/treatment groups who attrited post-treatment
d[(week1_attempted==1) & (week2_attempted==0),.N,keyby=control_first]
#No differen between control vs treatment groups
```

**Since the numbers of post-treatment attrited subjects in control vs treatment groups (week 1) are very close, we could assume that the missting values in week 2 are MCAR (missing completely at random). Therefore, we will use imputation to generate values for week 2 for the 5 subjects that completed week 1 test, but not week 2.** 

```{r}
completed <- d[week1_attempted==1]
completed
nrow(completed)
```

```{r}
#delete unnecessary columns
completed[ ,c('pre_task_control', 'pre_task_treat','w1_code','w2_code','first_language','test_language_guess','w207','w200','w209')] <- list(NULL)
```

```{r}
completed[week2_attempted==0]
```


```{r}
#replace 0's with NA so that imputation would replace NA's
completed$w2_t1_t2_mins[completed$w2_t1_t2_mins == 0] <- NA
completed$w2_total_mins[completed$w2_total_mins == 0] <- NA
completed$w2_score[completed$w2_score == 0] <- NA
```


```{r}
# print(md.pattern(completed))
```

```{r}
imputed <- mice(completed, m=5, maxit=50, meth='midastouch', seed=500)
```

```{r}
summary(imputed)
```


```{r}
#convering into dataframe
imputed_dataframe <- complete(imputed, 1)
```

```{r}
#convert into data table again
dt <- as.data.table(imputed_dataframe)
dt
```

```{r}
dt[w1_score < 40]
```

```{r}
dt[week2_attempted==0 & control_first==1]
```

```{r}
dt[week2_attempted==0 & control_first==0]
```


```{r}
#Number of subjects in control/treatment groups in week 1
dt[, .N, by=control_first]
```


```{r}
dt[, .('Avg Years Experience' = mean(years_experience)), keyby=control_first]
```


```{r}
dt$Control_w1 <- ifelse(dt$control_first == 1, "Y", "N")
group_mean <- dt[, .(mean(years_experience)), keyby=Control_w1]
```


```{r}
p<-ggplot(dt, aes(x=years_experience, color=Control_w1)) + 
  geom_histogram(fill="white", binwidth=0.5, alpha=0.5,position="dodge")
p+geom_vline(data=group_mean, aes(xintercept=V1, color=Control_w1),
             linetype="dashed") + labs(title="Years of Experience",x="Years", y = "Count") 

```


```{r}
dt[, .N, keyby=.(age, control_first)]
```


```{r}
p<-ggplot(dt, aes(x=age, color=Control_w1)) + 
  geom_bar(fill="white", alpha=0.5, width = 0.5, position="dodge")
# p + labs(title="Age of Subjects",x="Age Groups", y = "Count") + scale_y_discrete(limits=c(0,14), breaks=)
p + labs(title="Subjects' Age Groups",x="Age Groups", y = "Count") + ylim(0,15)
```


```{r}
dt[, .N, keyby=test_set_name]
```


```{r}
p<-ggplot(dt, aes(x=test_set_name)) + 
  geom_bar(color="darkblue",fill="lightblue", alpha=0.5, width = 0.5)
p + labs(title="Test Sets Used in the Study",x="Test Set", y = "Count") + 
  theme(axis.text.x = element_text(face="bold", size=12, angle=45, , hjust = 1), axis.text.y = element_text(size=12))
# p + labs(title="Subjects' Age Groups",x="Age Groups", y = "Count") + ylim(0,10)
```

```{r}
dt[, .N, keyby=.(team_size, control_first)]
```

```{r}
p<-ggplot(dt, aes(x=team_size, color=Control_w1)) + 
  geom_bar(fill="white", width=0.5, alpha=0.5,position="dodge")
p + labs(title="Team Sizes Where Subject Work",x="Team Size", y = "Count") 
```




```{r}
dt[, .('Average Week 1 Score' = mean(w1_score)), keyby=control_first]
```

```{r}
score_w1_mean <- dt[, .(mean(w1_score)), keyby=Control_w1]
```


```{r}
p<-ggplot(dt,  aes(x=w1_score, fill=Control_w1)) + geom_area(stat = "bin",alpha=0.6, binwidth=8)

p + geom_vline(data=score_w1_mean, aes(xintercept=V1, color=Control_w1),
             linetype="dashed") + labs(title="Average Week 1 Score",x="Score", y = "Count") 
```



```{r}
dt[, .('Average Week 2 Score' = mean(w2_score)), keyby=control_first]
```
```{r}
score_w2_mean <- dt[, .(mean(w2_score)), keyby=Control_w1]
score_w2_mean
```


```{r}
p<-ggplot(dt,  aes(x=w2_score, fill=Control_w1)) + geom_area(stat = "bin",alpha=0.6, binwidth=8)

p + geom_vline(data=score_w2_mean, aes(xintercept=V1,color=Control_w1), linetype="dashed") + ylim(0,30) + 
  labs(title="Average Week 2 Score",x="Score", y = "Count") 

```

```{r}
plot1 <- ggplot(dt, aes(Control_w1, w1_t1_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 1, Week 1",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot2 <- ggplot(dt, aes(Control_w1, w1_t1_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 1, Week 1",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot3 <- ggplot(dt, aes(Control_w1, w1_t2_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 2, Week 1",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot4 <- ggplot(dt, aes(Control_w1, w1_t2_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 2, Week 1",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot5 <- ggplot(dt, aes(Control_w1, w1_t3_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 3, Week 1",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot6 <- ggplot(dt, aes(Control_w1, w1_t3_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 3, Week 1",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot7 <- ggplot(dt, aes(Control_w1, w1_t1_t2_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 3, Week 1",
         x="Total Time for Tests 1 & 2, Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))


grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2, nrow=3)
```

```{r}
plot8 <- ggplot(dt, aes(Control_w1, w1_total_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Total Test Time, Week 1",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10),
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot9 <- ggplot(dt, aes(Control_w1, w1_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Total Score, Week 1",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10),
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))

grid.arrange(plot8, plot9, ncol=2, nrow=1)
```

```{r}
plot1 <- ggplot(dt, aes(Control_w1, w2_t1_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 1, Week 2",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot2 <- ggplot(dt, aes(Control_w1, w2_t1_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 1, Week 1",
         x="In Control Group During Week 2",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot3 <- ggplot(dt, aes(Control_w1, w2_t2_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 2, Week 2",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot4 <- ggplot(dt, aes(Control_w1, w2_t2_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 2, Week 2",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot5 <- ggplot(dt, aes(Control_w1, w2_t3_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 3, Week 2",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot6 <- ggplot(dt, aes(Control_w1, w2_t3_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 3, Week 2",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))


grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2, nrow=3)
```

```{r}
plot8 <- ggplot(dt, aes(Control_w1, w2_total_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Total Test Time, Week 2",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10),
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot9 <- ggplot(dt, aes(Control_w1, w2_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Total Score, Week 2",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10),
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))

grid.arrange(plot8, plot9, ncol=2, nrow=1)
```


1] "Variables:"
 [1] "subject_id"          "test_set_name"       "w1_code"             "w2_code"            
 [5] "control_first"       "week1_attempted"     "week2_attempted"     "berkeley_student"   
 [9] "upwork"              "upwork_20dollars"    "pre_task_control"    "pre_task_treat"     
[13] "w1_t1_id"            "w1_t1_mins"          "w1_t1_score"         "w1_t2_id"           
[17] "w1_t2_mins"          "w1_t2_score"         "w1_t3_id"            "w1_t3_mins"         
[21] "w1_t3_score"         "w1_t1_t2_mins"       "w1_total_mins"       "w1_score"           
[25] "w2_t1_id"            "w2_t1_mins"          "w2_t1_score"         "w2_t2_id"           
[29] "w2_t2_mins"          "w2_t2_score"         "w2_t3_id"            "w2_t3_mins"         
[33] "w2_t3_score"         "w2_t1_t2_mins"       "w2_total_mins"       "w2_score"           
[37] "years_experience"    "w200"                "w207"                "w209"               
[41] "first_language"      "test_language_guess" "team_size"           "age"


```{r}
dt[control_first==1, control_score := w1_score]
dt[control_first==1, treatment_score := w2_score]
dt[control_first==0, control_score := w2_score]
dt[control_first==0, treatment_score := w1_score]
dt[, .('Average Control Score' = mean(control_score), 'Average Treatment Score' = mean(treatment_score))]
```

```{r}
dt[, .('Average Control Score' = mean(control_score), 'Average Treatment Score' = mean(treatment_score)), keyby=.(upwork)]
```


```{r}
dt[control_first==1, control_time := w1_t1_t2_mins]
dt[control_first==1, treatment_time := w2_t1_t2_mins]
dt[control_first==0, control_time := w2_t1_t2_mins]
dt[control_first==0, treatment_time := w1_t1_t2_mins]
dt[, .('Average Control Time for First 2 Tasks' = mean(control_time), 'Average Treatment Time for First 2 Tasks' = mean(treatment_time))]
```

```{r}
dt[, .('Average Control Time for First 2 Tasks' = mean(control_time), 'Average Treatment Time for First 2 Tasks' = mean(treatment_time)), keyby=control_first]
```

```{r}
dt[week1_attempted == 1, .('Week 1 Score' = mean(w1_score), 'Week 1 Time' = mean(w1_t1_t2_mins)), keyby=control_first]
```


```{r}
dt[week2_attempted==1, .('Week 2 Score' = mean(w2_score), 'Week 2 Time' = mean(w2_t1_t2_mins)), keyby=.(upwork, control_first)]
```

```{r}
dt[week1_attempted == 1, .N, keyby=upwork]
```


```{r}
par(mfrow=c(4, 2))
for (val in unique(dt$test_set_name)) {
  both_attempted[test_set_name==val, hist(w1_t2_score, breaks = 10, main=val)]
}
```

```{r}
par(mfrow=c(4, 2))
for (val in unique(dt$test_set_name)) {
  both_attempted[test_set_name==val, hist(w2_t2_score, breaks = 10, main=val)]
}
```



```{r}
dt[control_first == 1, score_diff := w2_score - w1_score]
dt[control_first == 0, score_diff := w1_score - w2_score]
dt[control_first == 1, mins_diff := w2_t1_t2_mins - w1_t1_t2_mins]
dt[control_first == 0, mins_diff := w1_t1_t2_mins - w2_t1_t2_mins]

dt[, mean(score_diff)]
dt[, mean(mins_diff)]
dt[upwork == 0, mean(score_diff)]
dt[upwork == 1, mean(score_diff)]
dt[upwork == 0, mean(mins_diff)]
dt[upwork == 1, mean(mins_diff)]
```


```{r}
names(dt)
```

## Regressions

```{r}
temp <- dt[week2_attempted==1]
temp
```

```{r}
summary(lm(score_diff ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, temp))
# summary(lm(w2_t1_score ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, temp))

```

```{r}
summary(lm(w1_score ~ control_first +  upwork + I(upwork * control_first), dt))
```


```{r}
summary(lm(score_diff ~ upwork + control_first, dt))
```

```{r}
summary(lm(score_diff ~ control_first, dt))
```

```{r}
summary(lm(w2_score ~ control_first + upwork, dt))
```


```{r}
#PR
#look at difference betwwen difficulty levels of questions in week 2
summary(lm(w2_score ~ control_first + upwork, dt))
```

```{r}
#PR
#look at difference betwwen difficulty levels of questions in week 2
summary(lm(score_diff ~ control_first + upwork, dt))
```

```{r}
summary(lm(score_diff ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
```

```{r}
#within subject
modelAOV <- aov(score_diff ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt)
print(summary(modelAOV))
# demo1.aov <- aov(score_diff ~  control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, data= dt)
# summary(demo1.aov)
```
```{r}
summary(lm(w1_t1_t2_mins ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
```
```{r}
summary(lm(w1_score ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
```

```{r}
summary(lm(w2_score ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
```

