---
title: "Coding Experiment EDA | W241 Final Project"
author: "Arunima Kayath, Daniel Rasband, Payman Rhogani"
date: \today
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(data.table)
library(magrittr)
library(ggplot2)
library(ggthemes)
library(devtools)
library(mice) #for missing value imputation
library(reshape2)
library(gridExtra)
library(stargazer)
```


```{r}
data <- read.csv("CodingExperimentFinalResults.csv")
d <- as.data.table(data)
d
```


```{r}
#PR
print(paste("Number of subjects randomized for the study:", nrow(d)))
print(paste("Number of variables:", ncol(d)))
```

```{r}
print("Variables:")
names(d)
```

```{r}
#Number of subjects in control/treatment groups in week 1
d[, .N, by=control_first]
```


```{r}
#Week 1 participants
d[, .N, by=week1_attempted]
```


```{r}
#Week 2 participants
d[, .N, by=week2_attempted]
```
```{r}
print(paste("Number of subjects who attempted both tests (week 1 and 2):", d[(week1_attempted==1) & (week2_attempted==1), .N]))
```

```{r}
print(paste("Pre-treatment attrition:", nrow(d[week1_attempted == 0])))
print(paste("Post-treatment attrition:", nrow(d[(week1_attempted==1) & (week2_attempted==0)])))
```

```{r}
#Number of subjects in control/treatment groups who attrited pre-treatment
d[(week1_attempted==0) & (week2_attempted==0),.N,keyby=control_first]
#No differen between control vs treatment groups
```

```{r}
#Number of subjects in control/treatment groups who attrited post-treatment
d[(week1_attempted==1) & (week2_attempted==0),.N,keyby=control_first]
#No differen between control vs treatment groups
```

```{r}
dt <- d[(week1_attempted==1) & (week2_attempted==1)]
dt
```



```{r}
dt[, .('Avg Years Experience' = mean(years_experience)), keyby=control_first]
```


```{r}
dt$Control_w1 <- ifelse(dt$control_first == 1, "Y", "N")
group_mean <- dt[, .(mean(years_experience)), keyby=Control_w1]
```


```{r}
p<-ggplot(dt, aes(x=years_experience, color=Control_w1)) + 
  geom_histogram(fill="white", binwidth=0.5, alpha=0.5,position="dodge")
p+geom_vline(data=group_mean, aes(xintercept=V1, color=Control_w1),
             linetype="dashed") + labs(title="Years of Experience",x="Years", y = "Count") 

```


```{r}
dt[, .N, keyby=.(age, control_first)]
```


```{r}
p<-ggplot(dt, aes(x=age, color=Control_w1)) + 
  geom_bar(fill="white", alpha=0.5, width = 0.5, position="dodge")
# p + labs(title="Age of Subjects",x="Age Groups", y = "Count") + scale_y_discrete(limits=c(0,14), breaks=)
p + labs(title="Subjects' Age Groups",x="Age Groups", y = "Count") + ylim(0,15)
```


```{r}
dt[, .N, keyby=test_set_name]
```


```{r}
p<-ggplot(dt, aes(x=test_set_name)) + 
  geom_bar(color="darkblue",fill="lightblue", alpha=0.5, width = 0.5)
p + labs(title="Test Sets Used in the Study",x="Test Set", y = "Count") + 
  theme(axis.text.x = element_text(face="bold", size=12, angle=45, , hjust = 1), axis.text.y = element_text(size=12))
# p + labs(title="Subjects' Age Groups",x="Age Groups", y = "Count") + ylim(0,10)
```

```{r}
dt[, .N, keyby=.(team_size, control_first)]
```

```{r}
p<-ggplot(dt, aes(x=team_size, color=Control_w1)) + 
  geom_bar(fill="white", width=0.5, alpha=0.5,position="dodge")
p + labs(title="Team Sizes Where Subject Work",x="Team Size", y = "Count") 
```




```{r}
dt[, .('Average Week 1 Score' = mean(w1_score)), keyby=control_first]
```

```{r}
score_w1_mean <- dt[, .(mean(w1_score)), keyby=Control_w1]
```


```{r}
p<-ggplot(dt,  aes(x=w1_score, fill=Control_w1)) + geom_area(stat = "bin",alpha=0.6, binwidth=8)

p + geom_vline(data=score_w1_mean, aes(xintercept=V1, color=Control_w1),
             linetype="dashed") + labs(title="Average Week 1 Score",x="Score", y = "Count") 
```



```{r}
dt[, .('Average Week 2 Score' = mean(w2_score)), keyby=control_first]
```
```{r}
score_w2_mean <- dt[, .(mean(w2_score)), keyby=Control_w1]
score_w2_mean
```


```{r}
p<-ggplot(dt,  aes(x=w2_score, fill=Control_w1)) + geom_area(stat = "bin",alpha=0.6, binwidth=8)

p + geom_vline(data=score_w2_mean, aes(xintercept=V1,color=Control_w1), linetype="dashed") + ylim(0,30) + 
  labs(title="Average Week 2 Score",x="Score", y = "Count") 

```

```{r}
plot1 <- ggplot(dt, aes(Control_w1, w1_t1_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 1, Week 1",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot2 <- ggplot(dt, aes(Control_w1, w1_t1_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 1, Week 1",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot3 <- ggplot(dt, aes(Control_w1, w1_t2_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 2, Week 1",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot4 <- ggplot(dt, aes(Control_w1, w1_t2_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 2, Week 1",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot5 <- ggplot(dt, aes(Control_w1, w1_t3_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 3, Week 1",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot6 <- ggplot(dt, aes(Control_w1, w1_t3_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 3, Week 1",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot7 <- ggplot(dt, aes(Control_w1, w1_t1_t2_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 3, Week 1",
         x="Total Time for Tests 1 & 2, Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))


grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2, nrow=3)
```

```{r}
plot8 <- ggplot(dt, aes(Control_w1, w1_total_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Total Test Time, Week 1",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10),
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot9 <- ggplot(dt, aes(Control_w1, w1_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Total Score, Week 1",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10),
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))

grid.arrange(plot8, plot9, ncol=2, nrow=1)
```

```{r}
plot1 <- ggplot(dt, aes(Control_w1, w2_t1_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 1, Week 2",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot2 <- ggplot(dt, aes(Control_w1, w2_t1_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 1, Week 1",
         x="In Control Group During Week 2",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot3 <- ggplot(dt, aes(Control_w1, w2_t2_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 2, Week 2",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot4 <- ggplot(dt, aes(Control_w1, w2_t2_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 2, Week 2",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot5 <- ggplot(dt, aes(Control_w1, w2_t3_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Time to Complete Test 3, Week 2",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot6 <- ggplot(dt, aes(Control_w1, w2_t3_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Score: Test 3, Week 2",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10), 
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10), 
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))


grid.arrange(plot1, plot2, plot3, plot4, plot5, plot6, ncol=2, nrow=3)
```

```{r}
plot8 <- ggplot(dt, aes(Control_w1, w2_total_mins)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Total Test Time, Week 2",
         x="In Control Group During Week 1",
         y="Minutes") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10),
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))
plot9 <- ggplot(dt, aes(Control_w1, w2_score)) + geom_boxplot(varwidth=T,aes(fill=Control_w1)) +
    labs(title="Total Score, Week 2",
         x="In Control Group During Week 1",
         y="Score") + theme(axis.text.x = element_text(size = 10),axis.text.y = element_text(size = 10),
         axis.title.x = element_text(size = 10),axis.title.y = element_text(size = 10),
         legend.text = element_text(size=10), legend.title = element_text(size=8), plot.title = element_text(size=10)) +
         guides(fill=guide_legend(title="Control, \nwk 1"))

grid.arrange(plot8, plot9, ncol=2, nrow=1)
```

```{r}
# dt[control_first==1, control_score := w1_score]
# dt[control_first==1, treatment_score := w2_score]
# dt[control_first==0, control_score := w2_score]
# dt[control_first==0, treatment_score := w1_score]
# dt[, .('Average Control Score' = mean(control_score), 'Average Treatment Score' = mean(treatment_score))]
```

```{r}
# dt[, .('Average Control Score' = mean(control_score), 'Average Treatment Score' = mean(treatment_score)), keyby=.(upwork)]
```

```{r}
names(dt)
```


```{r}
dt[control_first==1, control_time_total := w1_total_mins]
dt[control_first==1, treatment_time_total := w2_total_mins]
dt[control_first==0, control_time_total := w1_total_mins]
dt[control_first==0, treatment_time_total := w2_total_mins]

dt[control_first==1, control_time_t1_t2 := w1_t1_t2_mins]
dt[control_first==1, treatment_time_t1_t2 := w2_t1_t2_mins]
dt[control_first==0, control_time_t1_t2 := w2_t1_t2_mins]
dt[control_first==0, treatment_time_t1_t2 := w1_t1_t2_mins]

dt[, .('Average Control Time for All Tasks' = mean(control_time_total), 'Average Treatment Time for All Tasks' = mean(treatment_time_total))]
dt[, .('Average Control Time for First 2 Tasks' = mean(control_time_t1_t2), 'Average Treatment Time for First 2 Tasks' = mean(treatment_time_t1_t2))]

```

```{r}
# dt[, .('Average Control Time for First 2 Tasks' = mean(control_time), 'Average Treatment Time for First 2 Tasks' = mean(treatment_time)), keyby=control_first]
```

```{r}
dt[week1_attempted == 1, .('Week 1 Score' = mean(w1_score), 'Week 1 Time' = mean(w1_t1_t2_mins)), keyby=control_first]
```


```{r}
dt[week2_attempted==1, .('Week 2 Score' = mean(w2_score), 'Week 2 Time' = mean(w2_t1_t2_mins)), keyby=.(upwork, control_first)]
```

```{r}
dt[week1_attempted == 1, .N, keyby=upwork]
```


```{r}
# par(mfrow=c(4, 2))
# for (val in unique(dt$test_set_name)) {
#   both_attempted[test_set_name==val, hist(w1_t2_score, breaks = 10, main=val)]
# }
```

# ```{r}
# par(mfrow=c(4, 2))
# for (val in unique(dt$test_set_name)) {
#   both_attempted[test_set_name==val, hist(w2_t2_score, breaks = 10, main=val)]
# }
# ```



```{r}
dt[control_first == 1, score_diff := w2_score - w1_score]
dt[control_first == 0, score_diff := w1_score - w2_score]
dt[control_first == 1, mins_diff := w2_total_mins - w1_total_mins]
dt[control_first == 0, mins_diff := w1_total_mins - w2_total_mins]

print(paste("Avg score difference:", dt[, mean(score_diff)]))
print(paste("Avg time difference:", dt[, mean(mins_diff)]))

# dt[upwork == 0, mean(score_diff)]
# dt[upwork == 1, mean(score_diff)]
# dt[upwork == 0, mean(mins_diff)]
# dt[upwork == 1, mean(mins_diff)]
```

```{r}
dt[control_first == 1, score_diff_t1 := w2_t1_score - w1_t1_score]
dt[control_first == 0, score_diff_t1 := w1_t1_score - w2_t1_score]
dt[control_first == 1, mins_diff_t1 := w2_t1_mins - w1_t1_mins]
dt[control_first == 0, mins_diff_t1 := w1_t1_mins - w2_t1_mins]

dt[control_first == 1, score_diff_t2 := w2_t2_score - w1_t2_score]
dt[control_first == 0, score_diff_t2 := w1_t2_score - w2_t2_score]
dt[control_first == 1, mins_diff_t2 := w2_t2_mins - w1_t2_mins]
dt[control_first == 0, mins_diff_t2 := w1_t2_mins - w2_t2_mins]

dt[control_first == 1, score_diff_t3 := w2_t3_score - w1_t3_score]
dt[control_first == 0, score_diff_t3 := w1_t3_score - w2_t3_score]
dt[control_first == 1, mins_diff_t3 := w2_t3_mins - w1_t3_mins]
dt[control_first == 0, mins_diff_t3 := w1_t3_mins - w2_t3_mins]

```

```{r}
dt[,score_diff_t1_t2 := score_diff_t1 + score_diff_t2]
dt[,mins_diff_t1_t2 := mins_diff_t1 + mins_diff_t2]
```


```{r}
dt[control_first == 1, treatment_score_t1 := w2_t1_score]
dt[control_first == 0, treatment_score_t1 := w1_t1_score]
dt[control_first == 1, control_score_t1 := w1_t1_score]
dt[control_first == 0, control_score_t1 := w2_t1_score]
dt[control_first == 1, treatment_mins_t1 := w2_t1_mins]
dt[control_first == 0, treatment_mins_t1 := w1_t1_mins]
dt[control_first == 1, control_mins_t1 := w1_t1_mins]
dt[control_first == 0, control_mins_t1 := w2_t1_mins]

dt[control_first == 1, treatment_score_t2 := w2_t2_score]
dt[control_first == 0, treatment_score_t2 := w1_t2_score]
dt[control_first == 1, control_score_t2 := w1_t2_score]
dt[control_first == 0, control_score_t2 := w2_t2_score]
dt[control_first == 1, treatment_mins_t2 := w2_t2_mins]
dt[control_first == 0, treatment_mins_t2 := w1_t2_mins]
dt[control_first == 1, control_mins_t2 := w1_t2_mins]
dt[control_first == 0, control_mins_t2 := w2_t2_mins]

dt[control_first == 1, treatment_score_t3 := w2_t3_score]
dt[control_first == 0, treatment_score_t3 := w1_t3_score]
dt[control_first == 1, control_score_t3 := w1_t3_score]
dt[control_first == 0, control_score_t3 := w2_t3_score]
dt[control_first == 1, treatment_mins_t3 := w2_t3_mins]
dt[control_first == 0, treatment_mins_t3 := w1_t3_mins]
dt[control_first == 1, control_mins_t3 := w1_t3_mins]
dt[control_first == 0, control_mins_t3 := w2_t3_mins]

dt[control_first == 1, treatment_score_t1_t2 := w2_t1_score + w2_t2_score]
dt[control_first == 0, treatment_score_t1_t2 := w1_t1_score + w1_t2_score]
dt[control_first == 1, control_score_t1_t2 := w1_t1_score + w1_t2_score]
dt[control_first == 0, control_score_t1_t2 := w2_t1_score + w2_t2_score]
dt[control_first == 1, treatment_mins_t1_t2 := w2_t1_t2_mins]
dt[control_first == 0, treatment_mins_t1_t2 := w1_t1_t2_mins]
dt[control_first == 1, control_mins_t1_t2 := w1_t1_t2_mins]
dt[control_first == 0, control_mins_t1_t2 := w2_t1_t2_mins]

dt[control_first == 1, treatment_score_total := w2_score]
dt[control_first == 0, treatment_score_total := w1_score]
dt[control_first == 1, control_score_total := w1_score]
dt[control_first == 0, control_score_total := w2_score]
dt[control_first == 1, treatment_mins_total := w2_total_mins]
dt[control_first == 0, treatment_mins_total := w1_total_mins]
dt[control_first == 1, control_mins_total := w1_total_mins]
dt[control_first == 0, control_mins_total := w2_total_mins]
```


```{r}
names(dt)
```

```{r}
dt
```

## Regressions and other tests

```{r}
# t.test(dt$treatment_score_total, dt$control_score_total, paired=TRUE)
# t.test(dt$treatment_mins_total, dt$control_mins_total, paired=TRUE)
# t.test(dt$control_mins_t1_t2, dt$treatment_mins_t1_t2, paired=TRUE)
# t.test(dt$control_score_t1_t2, dt$treatment_score_t1_t2, paired=TRUE)
# t.test(dt$control_score_t1, dt$treatment_score_t1, paired=TRUE)
# t.test(dt$control_mins_t1, dt$treatment_mins_t1, paired=TRUE)
# t.test(dt$control_score_t2, dt$treatment_score_t2, paired=TRUE)
# t.test(dt$control_mins_t2, dt$treatment_mins_t2, paired=TRUE)
# t.test(dt$control_score_t3, dt$treatment_score_t3, paired=TRUE)
# t.test(dt$control_mins_t3, dt$treatment_mins_t3, paired=TRUE)
```

**All the t-tests above produce p-value > 0.5, so I think this tells us that there is no within subject treatment effect.**

**So we should probaly look at the effect of treatment assignment sequence and contorl vs treatment in week 1 and week 2 separately.**


```{r}
#within subject, consiering the effect of control vs treatment sequence
seq_time_lm <- lm(mins_diff_t1_t2 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt)
seq_score_lm <- lm(score_diff_t1_t2 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt)
```

```{r}
# stargazer(seq_time_lm, seq_score_lm, type="text", font.size = "Huge")
```

```{r}
#within subject, consiering the effect of control vs treatment sequence. for Compliers
seq_time_lm_c <- lm(mins_diff_t1_t2 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt[(pre_task_control == 1) & (pre_task_treat == 1)])
seq_score_lm_c <- lm(score_diff_t1_t2 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt[(pre_task_control == 1) & (pre_task_treat == 1)])
# stargazer(seq_time_lm, seq_score_lm, type="text")
```



```{r}
#single variable
seq_time_lm2 <- lm(mins_diff_t1_t2 ~ control_first, dt)
seq_score_lm2 <- lm(score_diff_t1_t2 ~ control_first, dt)
seq_time_lm_c2 <- lm(mins_diff_t1_t2 ~ control_first, dt[(pre_task_control == 1) & (pre_task_treat == 1)])
seq_score_lm_c2 <- lm(score_diff_t1_t2 ~ control_first, dt[(pre_task_control == 1) & (pre_task_treat == 1)])
```

```{r}
stargazer(seq_time_lm, seq_score_lm, seq_time_lm_c, seq_score_lm_c, column.labels = c("All Subjects","All Subjects","Compliers","Compliers"), covariate.labels= "Control Group, wk1", type="text")
```

```{r}
stargazer(seq_time_lm2, seq_score_lm2, seq_time_lm_c2, seq_score_lm_c2, column.labels = c("All Subjects","All Subjects","Compliers","Compliers"), covariate.labels= "Control Group, wk1", type="text")
```


```{r}
#within subject, consiering the effect of control vs treatment sequence
summary(lm(score_diff ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
```


```{r}
#within subject, consiering the effect of control vs treatment sequence
summary(lm(mins_diff ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
```






```{r}
#within subject, consiering the effect of control vs treatment sequence

summary(lm(score_diff_t1 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
#
# summary(lm(mins_diff_t1 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
# summary(lm(score_diff_t2 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))

# summary(lm(mins_diff_t2 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
# summary(lm(score_diff_t3 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
# summary(lm(mins_diff_t3 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
summary(lm(score_diff_t1_t2 ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
# summary(lm(mins_diff_t1_t2~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))

# add pre_treatment control vs treatment
```

```{r}
#effect of treatment in week 1
# summary(lm(w1_score ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
#effect of treatment in week 2
# summary(lm(w2_score ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))
summary(lm(w1_t2_score ~ control_first + upwork + berkeley_student + upwork_20dollars + years_experience + team_size +age, dt))

```


 [1] "subject_id"            "test_set_name"         "w1_code"               "w2_code"              
 [5] "control_first"         "week1_attempted"       "week2_attempted"       "berkeley_student"     
 [9] "upwork"                "upwork_20dollars"      "pre_task_control"      "pre_task_treat"       
[13] "w1_t1_id"              "w1_t1_mins"            "w1_t1_score"           "w1_t2_id"             
[17] "w1_t2_mins"            "w1_t2_score"           "w1_t3_id"              "w1_t3_mins"           
[21] "w1_t3_score"           "w1_t1_t2_mins"         "w1_total_mins"         "w1_score"             
[25] "w2_t1_id"              "w2_t1_mins"            "w2_t1_score"           "w2_t2_id"             
[29] "w2_t2_mins"            "w2_t2_score"           "w2_t3_id"              "w2_t3_mins"           
[33] "w2_t3_score"           "w2_t1_t2_mins"         "w2_total_mins"         "w2_score"             
[37] "years_experience"      "w200"                  "w207"                  "w209"                 
[41] "first_language"        "test_language_guess"   "team_size"             "age"                  
[45] "control_time_total"    "treatment_time_total"  "control_time_t1_t2"    "treatment_time_t1_t2" 
[49] "score_diff"            "mins_diff"             "score_diff_t1"         "mins_diff_t1"         
[53] "score_diff_t2"         "mins_diff_t2"          "score_diff_t3"         "mins_diff_t3"         
[57] "score_diff_t1_t2"      "mins_diff_t1_t2"       "treatment_score_t1"    "control_score_t1"     
[61] "treatment_mins_t1"     "control_mins_t1"       "treatment_score_t2"    "control_score_t2"     
[65] "treatment_mins_t2"     "control_mins_t2"       "treatment_score_t3"    "control_score_t3"     
[69] "treatment_mins_t3"     "control_mins_t3"       "treatment_score_t1_t2" "control_score_t1_t2"  
[73] "treatment_mins_t1_t2"  "control_mins_t1_t2"    "treatment_score_total" "control_score_total"  
[77] "treatment_mins_total"  "control_mins_total"





